### 2023-08-24 documents/sections/proto_carib.tex
fixes #22

Knowledge about the ancestral system makes evident that the divergent \hixka and \trio forms in \cref{tab:hixintro,tab:triintro} behave irregularly because they preserve the original \PC \gl{1}\gl{sa} prefix \rc{w-}; they are therefore \firstmention{conservative}.
They contrast with regular \gl{sa} verbs, which are innovative in both languages.
The reflexes of \rc{w-} are \firstmention{relics}, old and restricted to a few lexemes, contrasting with the innovative prefixes found elsewhere.
These verbs and their prefixes are comparable with the few English nouns like \obj{ɒks}, which preserve the old plural suffix \obj{-ən}.
It was once more widespread as the normal plural suffix of the weak inflection, compare German \obj{ɔks-ən} \qu{ox-en}, \obj{naːmə-n} \qu{name-s}, \obj{haːzə-n} \qu{hare-s}, \obj{bɛːʁ-ən} \qu{bear-s}.
Since the regular \hixka and \trio prefixes are innovative, the question arises how they developed.

>>>>

Knowledge about the ancestral system makes it clear that the divergent \hixka and \trio forms in \cref{tab:hixintro,tab:triintro} behave irregularly because they preserve the original \PC \gl{1}\gl{sa} prefix \rc{w-}; they are therefore \firstmention{conservative}.
They contrast with regular \gl{sa} verbs, which are innovative in both languages.
The reflexes of \rc{w-} are \firstmention{relics}, old and restricted to a few lexemes, contrasting with the innovative prefixes found elsewhere.
These verbs and their prefixes are comparable with the few English nouns like \obj{ɒks}, which preserve the old plural suffix \obj{-ən}.
It was once more widespread as the normal plural suffix of the weak inflection, compare German \obj{ɔks-ən} \qu{oxen}, \obj{naːmə-n} \qu{names}, \obj{haːzə-n} \qu{hares}, \obj{bɛːʁ-ən} \qu{bears}.
Since the regular \hixka and \trio prefixes are innovative, the question arises how they developed.
